

```{r}

library(feather)
library(tidyverse)
library(mclust)
library(cluster)

data <- read_feather("results/data.feather")

```

### What's the most common license id

```{r}
top_lic <- data %>% 
  group_by(license_id) %>% 
  summarise(num = n()) %>% 
  arrange(desc(num))


head(top_lic,10)
```

### What's the most popular project? 
#### ranked by how many copies are in the dataset for each open source project id

```{r}

(top_uuid <- data %>% 
  group_by(d_r_uuid) %>% 
  summarise(num = n()) %>% 
  arrange(desc(num)) %>% 
  head(10))

```

### What's the most popular version for each of the top projects?

```{r}

data %>% 
  filter(d_r_uuid %in% top_uuid$d_r_uuid) %>% 
  group_by(d_r_uuid,version) %>% 
  summarise(num = n()) %>% 
  arrange(desc(num))

  
```

## Insight: Each d_r_uuid (open source project id) is associated with a unique version of a project. In other words, different versions of the same project will have different open source project ids.

combine levels based on their occurring frequency in the dataset.

```{r}
data$license_id <- as.factor(data$license_id)

dws_freq <- as.data.frame(table(data$dws))
names(dws_freq) <- c("dws","dwsfreq")

dns_freq <- as.data.frame(table(data$dns))
names(dns_freq) <- c("dns","dnsfreq")

so_freq <- as.data.frame(table(data$so))
names(so_freq) <- c("so","sofreq")

lic_freq <- as.data.frame(table(data$license_id))
names(lic_freq) <- c("license_id","licfreq")

combined <- inner_join(dws_freq,data,by="dws")
combined <- inner_join(dns_freq,combined,by = "dns")
combined <- inner_join(so_freq,combined,by = "so")
combined <- inner_join(lic_freq,combined,by = "license_id")

data_freq <- combined %>% 
  select(d_r_uuid, version, dwsfreq, dnsfreq, sofreq, licfreq)
```


```{r}
combined %>% 
  arrange(desc(dwsfreq)) %>% 
  head(10)

combined %>% 
  arrange(desc(dnsfreq)) %>% 
  head(10)

combined %>% 
  arrange(desc(sofreq)) %>% 
  head(10)

combined %>% 
  arrange(desc(licfreq)) %>% 
  head(10)

```

```{r}
combined %>% 
  group_by(so,dns) %>% 
  summarise(num = n()) %>% 
  arrange(desc(num)) %>% 
  View()
```



