---
title: "5 insights"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load dependencies}
library(feather)
library(dplyr)

data <- read_feather("../results/data.feather")
head(data)
```


### 1. Most popular projects by license ID

```{r Most popular projects by uuid version and license ID}
top_projects <- data %>% 
  group_by(d_r_uuid, version, license_id) %>% 
  summarize(count= n()) %>% 
  arrange(desc(count)) 
head(top_projects)
```

Open source project ID 3dec9166-bd9d-45d3-acae-9c78adb1a684, version 2.15.2 with license ID 45 is the most popular. It has 7393 observations.


### 2. Most popular projects by uuid and version only

```{r Most popular projects by uuid and version only}
top_projects2 <- data %>% 
  group_by(d_r_uuid, version) %>% 
  summarize(count= n()) %>% 
  arrange(desc(count)) 
head(top_projects2)
```

Open source project ID 2ff38a7c-238b-487f-af9b-64a2ec81d81c, verison 8u72-b15 (regardless of license types) is the most popular, It has 46680 observations.


### 4. Most common license ID used in this collection of open source projects

```{r Most common license ID used}
top_license <- data %>% 
  group_by(license_id) %>% 
  summarize(count= n()) %>% 
  arrange(desc(count)) 
head(top_license)
```

License ID 45 is the most commonly used license in this collection of open source projects. It has 439800 observations.


### 3. Most popular project by uuid only

```{r Most popular project by uuid only}
top_project3 <- data %>% 
  group_by(d_r_uuid) %>% 
  summarize(count= n()) %>% 
  arrange(desc(count)) 
head(top_project3)
```

Open source project ID 2ff38a7c-238b-487f-af9b-64a2ec81d81c (regardless of verison and license ID) is the most popular, It has 46680 observations. It is the same project when sorted by uuid and version.


### 5. Number of unpopular projects

```{r unpopular projects}
unpopular_project <- data %>% 
  group_by(d_r_uuid) %>% 
  summarize(count= n()) %>% 
  arrange() %>% 
  filter(count<=100)
count(unpopular_project)
```

There are 93830 projects (sorted by uuid) in this data set that have less than 100 observations. 
